Cybersecurity Is Too Important\\To Be Left To The Specialists

### 2019-03-16 FIE2019.tex
JHD edits, including Naiakshima

% JHD to
% a) Add the Bonn work
% b) Add ABET stuff and ask Tom P to cross-check.
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{paralist}
\usepackage{url}
\usepackage{enumitem}
\usepackage[hyphenbreaks]{breakurl}
\usepackage[T1]{fontenc}
\usepackage{booktabs} % For formal tables

@@

The Payments Industry \cite[6.6]{PCI2018b} insists on either independent code reviews by security specialists or a Web Application Firewall: essentially saying that the normal development process even after developers are trained in secure coding practices \cite[6.5]{PCI2018b} cannot be trusted to deliver secure code.

@@

But \cite[Table 1]{Ruiz2019a} shows that the UK situation is distinctly different: he quotes that 61\% of UK courses offer mandatory cybersecurity content, and his research was based on web scraping, it represents a lower bound.
\section{Policy Context}

@@

Is teaching Cybersecurity different? Lecturing is probably not the best way. Should we use real-life case studies (e.g. British Airways)

@@

\subsection{The case of Java}\label{sec:Java}
To the best of the authors' knowledge, no survey equivalent to \cite{Drop2019} has been done for Java textbooks. Indeed, many such books go nowhere near security applications.  But this means that the programmer who has to implement security is left to the documentation of the package/API being used, and to informal resources. \cite{Mengetal2018a} analysed 503 Cybersecurity-related postings on the popular Stack overflow (\url{https://stackoverflow.com}) resource.  53\% were about the Spring Security framework (\url{https://projects.spring.io/spring-security/}), dominated by authentication (45\%). The discussion \cite[\S4.3.1]{Mengetal2018a} of cross-site request forgery (CSRF) is especially worrying.  By default, Spring implcitly enables protection against this. But all the accepted answers to CSRF-related failures simply suggested disabling they check. There were no negative comments about this, and indeed a typical response is ``Adding \verb!csrf().disable()!
solved the issue!!! I have no idea why it was enabled by default''. As of writing (16 January 2018) there were no negative comments about this disabling of a vital security feature.
\par
This research was further developed by \cite{Chenetal2019a}  (and popularised in a security community in \cite{Zorz2019a}). Their first finding was
\begin{quote}
644 out of the 1,429 inspected answer posts
(45\%) are insecure, meaning that insecure suggestions
popularly exist on SO. Insecure answers dominate, in
particular, the SSL/TLS category [355 insecure versus 150 secure]].
\end{quote}

\subsection{Android}\label{sec:Android}
\cite{Fischeretal2017a} looked specifically at the use of resources from Stack Overflow in Android applications. Their key finding was this.
\begin{quote}
We found that 15.4\% of all 1.3 million Android applications
contained security-related code snippets from
Stack Overflow. Out of these 97.9\% contain at least one
insecure code snippet.
\end{quote}
We should note two caveats (in opposite directions). Their labelling was conservative, in that snippets were only labelled as insecure if that was demonstrable, and, for example, mere use of outdated SSL/TLS was not automatically deemed insecure. On the other hand, the insecure snippet might have been used in a way that did not expose the insecurity.
\par
The uncritical reading of Stack Overflow was also noted in \cite[Slide 29]{Votipkaetal2019a}. Their key recommendation  \cite[Slide 32]{Votipkaetal2019a} is ``Improve documentation: Clarify what you can(not) copy/paste''. 
\subsection{Staff}
It is well known that Cybersecurity skills are in short supply, for example \cite{Page2018a}.
\begin{quote}
% JHD: I am in touch with ESG to try to find more, and someUK-specific numbers.
Research into the state of IT conducted annually by ESG\footnote{Apparently \url{https://www.esg-global.com/research/esg-brief-2018-cybersecurity-spending-trends}.} has revealed that the skills gap in information security continues to widen and has doubled in the past five years. In 2014, 23\% of respondents to the survey stated that their organisation had a problematic shortage of information security skills. This had climbed to 51\% at the beginning of this year. Clearly, this is an issue which is being felt across many industries and organisations, and is a concern which extends beyond IT leadership into the boardroom.
\end{quote}
The ESG survey is international, but ESG have confirmed that the UK figures are very similar.
%JHD possibly to write about his recruitment experiences.  ? more IoC input?

@@

In recent years the BCS has evolved its Accreditation Practices to promote and mandate the inclusion of Cybersecurity within the programmes the body accredits. The timeline which this process has followed in Table \ref{table:1} .
\begin{center}
  \begin{table}[h!]
  \begin{tabular}{ | p{6cm} |p{1.5cm} |}
    \hline
    IV. ACCREDITATION:RQ3 - A. Developing Expectations &   \\ \hline
    UK Government Cybersecurity Strategy \cite{UKCabinetOffice} & November 2011 \\ \hline
    Three workshops of a consortium of industry, academia and government bodies - led by CPHC and (ISC)2 - leading to the development of Cybersecurity learning guidelines to be embedded into BCS accredited UK Computer Science and IT-related degree \cite{CPHCISC2}  & 2013 to June 2015 \\ \hline
    UK Government report Cybersecurity Skills, Business Perspectives and Government's Next Steps Report Released \cite{UKCabinetOffice2014} & March 2014  \\ \hline
    Council of Professors and Heads of Computing (CPHC) Identifies Cybersecurity as one the top 3 concerns in Computing & April 2014 \\ \hline
    Joint Development of White Paper from CPHC and The International Information Systems Security Certification Consortium(ISC)2 \cite{CPHCISC2014} & April -November 2014 \\ \hline
    Extended Cybersecurity Criteria included in BCS Accreditation Guidelines \cite{BCS2018a}& June 2015 \\
    \hline
    IV. ACCREDITATION:RQ3 - B. What does the BCS tell Universities? & \\ \hline
    Cybersecurity Principles Roadshow & March-April 2016 \\ \hline
    IV. ACCREDITATION:RQ3 - C. Accreditation - what progress has been made? &  \\ \hline
    All visited HEIs expected to be fully compliant & September 2020 (BCS follow a 5-year Accreditation Cycle)  \\ \hline
  \end{tabular}
  \caption{Timeline of the development of Cybersecurity expectations}
  \label{table:1}
  \end{table}
\end{center}
\subsection{Developing Expectations}
Internationally the expectations regarding both the breadth and depth of the expected Cybersecurity coverage has been the subject of much discussion, debate and analysis. Like many Governments, the UK Goverment has been actively been seeking ways to address this \cite{UKCabinetOffice}, \cite{UKCabinetOffice2014}. In parallel to the work complete by the ACM \cite{ACM2013a}, in the UK considerable effort was taken to ensure Industry, Higher Education, Government and the related Professional Bodies collaborated on a set of guidelines which are to the benefit of the various stakeholders and wider society \cite{Irons2016}. In 2013, an initiative was set up by (ISC)2, CPHC (the representative body of Computer Science Departments) and the Cabinet Office to examine embedding Cybersecurity into undergraduate degrees in the UK. Three workshops in 2013 and 2015 attempted to define the principles of Cybersecurity education and proposed a framework for embedding these principles in UK Computing Science curricula. Attendees at the workshops included industry, professional bodies, UK government departments and more than 30 Universities that offer undergraduate Computing Science degrees. This work intially lead to a white paper related to a proposal in the form of a whitepaper \cite{CPHCISC2014}, followed by a set of guidelines \cite{CPHCISC2}. The BCS agreed to adopt the outputs into their accreditation criteria. This was the first time that Cybersecurity has been extensively referenced within accreditation criteria for computing and IT-related degrees. The fact that Cybersecurity is included as a  component of the BCS accreditation criteria, reflects the importance placed on Cybersecurity and the expectation that all computing graduates should have knowledge and skills in Cybersecurity as they move towards Chartered status.

>>>>

% JHD to
% a) Add the Bonn work
% b) Add ABET stuff (done) and ask Tom P to cross-check.
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{paralist}
\usepackage{url}
\usepackage{enumitem}
\usepackage[hyphenbreaks]{breakurl}
\usepackage[T1]{fontenc}
\usepackage{booktabs} % For formal tables

@@

The Payments Industry \cite[6.6]{PCI2018b} insists on either independent code reviews by security specialists or a Web Application Firewall: essentially saying that the normal development process even after developers are trained in secure coding practices \cite[6.5]{PCI2018b} cannot be trusted to deliver secure code. This would seem to be particularly the case with ``agile'' processes \cite{Bartsch2011a}.

@@

But \cite[Table 1]{Ruiz2019a} shows that the UK situation is distinctly different: he quotes that 61\% of UK courses offer mandatory cybersecurity content, and his research was based on web scraping, it represents a lower bound.

It is at least plausible to attribute this difference to differences in the accreditation regimes.
\begin{description}
\item[UK]BCS has had cybersecurity in the curriculum since 2013, and required cybersecurity in accreditation since 2015 (Table \ref{table:1}), with the result that all accedited universities should be compliant by 2020 (because of the five-year cycle).
\item[US]ACM has equally had cybersecurity (``Information Assurance and Security'' --- IAS) in the curriculum since 2013 \cite{ACM2013a}, but it is not the accrediting body. ABET is, and is requiring IAS with effect from the 2019-20 cycle (self study reports due 1 Juy 2019) \cite[chapter 7]{Davenportminor2019a}.  % need a better reference
\end{description}
\section{Policy Context}

@@

Is teaching Cybersecurity different? Lecturing is probably not the best way. Should we use real-life case studies (e.g. British Airways \cite{Barth2018a})

@@

\subsection{The case of Java}\label{sec:Java}
To the best of the authors' knowledge, no survey equivalent to \cite{Drop2019} has been done for Java textbooks. Indeed, many such books go nowhere near security applications.  But this means that the programmer who has to implement security is left to the documentation of the package/API being used, and to informal resources. \cite{Mengetal2018a} analysed 503 Cybersecurity-related postings on the popular Stack overflow (\url{https://stackoverflow.com}) resource.  53\% were about the Spring Security framework (\url{https://projects.spring.io/spring-security/}), dominated by authentication (45\%). The discussion \cite[\S4.3.1]{Mengetal2018a} of cross-site request forgery (CSRF) is especially worrying.  By default, Spring implcitly enables protection against this. But all the accepted answers to CSRF-related failures simply suggested disabling they check. There were no negative comments about this, and indeed a typical response is ``Adding \verb!csrf().disable()!
solved the issue!!! I have no idea why it was enabled by default''. As of writing (16 January 2018) there were no negative comments about this disabling of a vital security feature.
\par
This research was further developed by \cite{Chenetal2019a}  (and popularised in a security community in \cite{Zorz2019a}). Their first finding was
\begin{quote}
644 out of the 1,429 inspected answer posts
(45\%) are insecure, meaning that insecure suggestions
popularly exist on SO. Insecure answers dominate, in
particular, the SSL/TLS category [355 insecure versus 150 secure, i.e. $>70$\%].
\end{quote}

\subsection{Android}\label{sec:Android}
\cite{Fischeretal2017a} looked specifically at the use of resources from Stack Overflow in Android applications. Their key finding was this.
\begin{quote}
We found that 15.4\% of all 1.3 million Android applications
contained security-related code snippets from
Stack Overflow. Out of these 97.9\% contain at least one
insecure code snippet.
\end{quote}
We should note two caveats (in opposite directions). Their labelling was conservative, in that snippets were only labelled as insecure if that was demonstrable, and, for example, mere use of outdated SSL/TLS was not automatically deemed insecure. On the other hand, the insecure snippet might have been used in a way that did not expose the insecurity.
\par
The uncritical reading of Stack Overflow was also noted in \cite[Slide 29]{Votipkaetal2019a}. Their key recommendation  \cite[Slide 32]{Votipkaetal2019a} is ``Improve documentation: Clarify what you can(not) copy/paste''. 
\subsection{Agile}
To the best of the authors' knowledge, no survey equivalent to \cite{Drop2019} has been done for ``Agile'' textbooks. It is the authors' experience that the vast majority of students' individual software projects are developed on Agile lines. Many authorshave found disconnects between Agile practices and secure software development: notably \cite{Bartsch2011a} for small projects and \cite{vanderHeijden:2018:EPS:3239235.3267426} for large projects.
\par
Agile's preference for functionality over non-functional requirements is clearly displayed in practice. \cite{Naiakshinaetal2017a} asked 20 student developers to imagine they
were part of a team working on creating a social networking site for
our university and to implement a password storage mechanism for this. 10 (``primed'') were explicitly told that the storage had to be secure and 10 (``unprimed'') were not. None of the unprimed ones implemented any security.
\subsection{Staff}
It is well known that Cybersecurity skills are in short supply, for example \cite{Page2018a}.
\begin{quote}
% JHD: I am in touch with ESG to try to find more, and someUK-specific numbers.
Research into the state of IT conducted annually by ESG\footnote{Apparently \url{https://www.esg-global.com/research/esg-brief-2018-cybersecurity-spending-trends}.} has revealed that the skills gap in information security continues to widen and has doubled in the past five years. In 2014, 23\% of respondents to the survey stated that their organisation had a problematic shortage of information security skills. This had climbed to 51\% at the beginning of this year. Clearly, this is an issue which is being felt across many industries and organisations, and is a concern which extends beyond IT leadership into the boardroom.
\end{quote}
The ESG survey is international, but ESG have confirmed that the UK figures are very similar.
%JHD possibly to write about his recruitment experiences.  ? more IoC input?

@@

In recent years the BCS has evolved its Accreditation Practices to promote and mandate the inclusion of Cybersecurity within the programmes the body accredits. The timeline which this process has followed in Table \ref{table:1}.
\begin{center}
  \begin{table}[h!]
  \begin{tabular}{ | p{6cm} |p{1.5cm} |}
    \hline
    IV. ACCREDITATION:RQ3 - A. Developing Expectations &   \\ \hline
    UK Government Cybersecurity Strategy \cite{UKCabinetOffice} & November 2011 \\ \hline
    Three workshops of a consortium of industry, academia and government bodies - led by CPHC and (ISC)2 - leading to the development of Cybersecurity learning guidelines to be embedded into BCS accredited UK Computer Science and IT-related degree \cite{CPHCISC2}  & 2013 to June 2015 \\ \hline
    UK Government report Cybersecurity Skills, Business Perspectives and Government's Next Steps Report Released \cite{UKCabinetOffice2014} & March 2014  \\ \hline
    Council of Professors and Heads of Computing (CPHC) Identifies Cybersecurity as one the top 3 concerns in Computing & April 2014 \\ \hline
    Joint Development of White Paper from CPHC and The International Information Systems Security Certification Consortium(ISC)2 \cite{CPHCISC2014} & April -November 2014 \\ \hline
    Extended Cybersecurity Criteria included in BCS Accreditation Guidelines \cite{BCS2018a}& June 2015 \\
    \hline
    IV. ACCREDITATION:RQ3 - B. What does the BCS tell Universities? & \\ \hline
    Cybersecurity Principles Roadshow & March-April 2016 \\ \hline
    IV. ACCREDITATION:RQ3 - C. Accreditation - what progress has been made? &  \\ \hline
    All visited HEIs expected to be fully compliant & September 2020 (BCS follow a 5-year Accreditation Cycle)  \\ \hline
  \end{tabular}
  \caption{Timeline of the development of Cybersecurity expectations}
  \label{table:1}
  \end{table}
\end{center}
\subsection{Developing Expectations}
Internationally the expectations regarding both the breadth and depth of the expected Cybersecurity coverage has been the subject of much discussion, debate and analysis. Like many Governments, the UK Goverment has been actively been seeking ways to address this \cite{UKCabinetOffice}, \cite{UKCabinetOffice2014}. In parallel to the work complete by the ACM \cite{ACM2013a}, in the UK considerable effort was taken to ensure Industry, Higher Education, Government and the related Professional Bodies collaborated on a set of guidelines which are to the benefit of the various stakeholders and wider society \cite{Irons2016}. In 2013, an initiative was set up by (ISC)2, CPHC (the representative body of Computer Science Departments) and the Cabinet Office to examine embedding Cybersecurity into undergraduate degrees in the UK. Three workshops in 2013 and 2015 attempted to define the principles of Cybersecurity education and proposed a framework for embedding these principles in UK Computing Science curricula. Attendees at the workshops included industry, professional bodies, UK government departments and more than 30 Universities that offer undergraduate Computing Science degrees. This work intially lead to a white paper related to a proposal in the form of a whitepaper \cite{CPHCISC2014}, followed by a set of guidelines \cite{CPHCISC2}. The BCS agreed to adopt the outputs into their accreditation criteria. This was the first time that Cybersecurity has been extensively referenced within accreditation criteria for computing and IT-related degrees. The fact that Cybersecurity is included as a  component of the BCS accreditation criteria, reflects the importance placed on Cybersecurity and the expectation that all computing graduates should have knowledge and skills in Cybersecurity as they move towards Chartered status.
